Optimal (Multiway) Spatial Joins

### 2024-05-27 msj.tex
yufei

The rest of the section will focus on how to prepare the sets $\dcross_H(\bm{t})$ of all $\bm{t} \in \J(R_1', ..., R_{k-2}')$ in $O(n \log n + k \cdot \out)$ time. An analogous method can be used to compute the sets $\dcross_V(\bm{t})$ of all $\bm{t}$ in the same time complexity.

@@

Finding the $\cross_H(r^*)$ sets of all $r^* \in R^*_i$ is an instance of the find-all-sorted version of Problem $\mathscr{D}$ (with $H$ and $R^*_i$ as the input). Statement (1) of Lemma~\ref{lmm:hv:type1:cross-r*}, as well as the discussion in Section~\ref{sec:bricks}, assures us that the total time to do so for all $R^*_1, ..., R^*_{k-2}$ is bounded by $O(n \log n + \out)$. Note that, for each $\cross_H(r^*)$ computed, the (horizontal) segments therein has been sorted in ascending order of y-coordinate.

>>>>

The rest of the section will focus on how to prepare the sets $\dcross_H(\bm{t})$ of all $\bm{t} \in \J(R_1', ..., R_{k-2}')$ in $O(n \log n + k \cdot \out)$ time. An analogous method can be used to compute the sets $\dcross_V(\bm{t})$ of all $\bm{t}$ within the same time complexity.

@@

Finding the $\cross_H(r^*)$ sets of all $r^* \in R^*_i$ is an instance of the find-all-sorted version of Problem $\mathscr{D}$ (with $H$ and $R^*_i$ as the input). Statement (1) of Lemma~\ref{lmm:hv:type1:cross-r*}, as well as the discussion in Section~\ref{sec:bricks}, assures us that the total time to do so for all $R^*_1, ..., R^*_{k-2}$ is bounded by $O(k n \log n + \out)$. Note that, for each $\cross_H(r^*)$ computed, the (horizontal) segments therein has been sorted in ascending order of y-coordinate.
